Getting Started
===============

This document will show you how to get up and running with Read the Docs.
You will have your docs imported on Read the Docs in 5 minutes,
displayed beautifully for the world.

Install GWHAT
-------------

WHAT can run on Windows, Linux, or OS X computer operating systems. However, a stand-alone executable
of the program is currently released and tested only for the Windows 7 platform. This executable
should also be compatible with Windows XP. For the Linux and OS X platforms, the software can be
run directly from the source code, provided that Python 2.7 and all the required third party packages are
installed on the computer (PySide, NumPy, matplotlib, xlrd, xlwt).
The stand-alone executable for Windows 7 is distributed in a Zip archive that can be downloaded
freely on GitHub (https://github.com/jnsebgosselin/WHAT/releases). This archive
contains:

- the GNU General Public License;
- a folder named “WHAT” that contains all the necessary system files for the program to run, including
the file “WHAT.exe” from which the software can be started;
- a folder named “Projects” where all input and output files used or created by WHAT are stored by
default. This folder includes samples of input and output files that provide a quick and convenient
way to test and learn the various features of the program.

Once the content of the Zip archive has been extracted, the program can be started directly from
the “WHAT.exe” executable file that is contained within the folder named “WHAT”. The software can
conveniently run from any location on the computer or from any storage device without the need to install
the program beforehand.

Update GWHAT
------------

It is possible to update WHAT by downloading the Zip archive of a later version of the software,
extracting the content, and by manually overwriting the “WHAT” folder of the older version with the
newer one that was just downloaded.